### 2015-07-09 narrative/proposed-work.tex
more changes for readability.

>>>>

One of the underlying principles of our approach is that we recognize that there are a small set
of important I/O patterns to optimize for~\cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
and our representative applications have worked with us on all of these I/O patterns. Throughout our project
we will continuously focus on creating research artifacts which can optimize these patterns on current generation through
exascale systems.  One important pattern is Checkpoint/Restarts (CR) and we will focus on optimizing these through our
research, and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing 
the CR data. The migration and purging of this will be optimized by our SSIO layer, and we will have the user data intentions
signify the utility of CR data so that this data can be high-priority but stored for short periods of time.

### 2015-07-09 narrative/qos.tex
more changes for readability.

\subsubsection{Resource Management}
There is an important connection between finding the resources
that can fulfill a particular request and the performance predictability of that request. As such, this demands
careful resource management strategies that can deal with placement and retrieval of 
a large number of data chunks spread across the entire storage hierarchy. 
%This connection is particularly important for data retrieval 
%- in large scale storage systems, finding a resource to read can be a significant, if not dominant, 
%component of overall read latency. 
Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because they require a single entity that tracks updates in the system. 
Traditional file systems are good examples for this ; most updates to files require updates 
to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, searchs for 
resources at request time. Pile systems allow very efficient writes because clients can write wherever
there is free space and there is very low bookkeeping overhead. However, unbounded search in pile systems
is possible, e.g., when it is unclear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
partitioning of the search space and a method to limit the search to a small number of partitions.

>>>>

\subsubsection{(Resource Management}
There is an important connection between finding the resources
that can fulfill a particular request and the performance predictability of that request. As such, this demands
careful resource management strategies that can deal with placement and retrieval of 
a large number of data chunks spread across the entire storage hierarchy. 
%This connection is particularly important for data retrieval 
%- in large scale storage systems, finding a resource to read can be a significant, if not dominant, 
%component of overall read latency. 
Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because they require a single entity that tracks updates in the system. 
Traditional file systems are good examples for this ; most updates to files require updates 
to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, searchs for 
resources at request time. Pile systems allow very efficient writes because clients can write wherever
there is free space and there is very low bookkeeping overhead. However, unbounded search in pile systems
is possible, e.g., when it is unclear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
partitioning of the search space and a method to limit the search to a small number of partitions.
